Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.8)} \underline{Drafting Committee: DC90 (\today)}

### 2011-03-01 summary.tex
updated summary

Beam helicity and beam charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.

A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The \blue{resulting} \blue{beam charge} asymmetry amplitudes represent the statistically \blue{most} precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this simultaneous extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic of the beam charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data. \blue{This model fit ~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 Ref.~\cite{Air09}. \blue{The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.}

>>>>

Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. \blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained 1996-2005 experimental period \blue{described in} Ref.~\cite{Air09}}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. \blue{This model fit~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}. The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. All amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$. No localised features are observed in any particular $t$-bin.
